A Data-Driven Framework for Neural Field Modelling

### 2011-03-11 ltx/BrainIDEPoster/BrainIDE_Poster.tex
poster edits
made a colour change in the poster
added BrainIDETalk

\setbeamercolor{block title}{fg=ngreen,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10}

@@

\institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Australia \\
% 2. The Bionic Ear Institute, East Melbourne, VIC, Australia \\
% 3. Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK \\
2. Department of Automatic Control and Systems Engineering, University of Sheffield, UK \\
3. Department of Applied Physics and Applied Mathematics, Columbia University, USA \\
4. Department of Systems and Control Engineering, University of Malta, Malta }

%-----------------------------------------------------------
% Start the poster itself
%-----------------------------------------------------------
% The \rmfamily command is used frequently throughout the poster to force a serif font to be used for the body text
% Serif font is better for small text, sans-serif font is better for headers (for readability reasons)
%-----------------------------------------------------------
\begin{document}
\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top
	  \setbeamercolor{block title}{fg=red,bg=white}%frame color

@@

		The minimum distance between basis functions must also satisfy 
		\begin{equation}\label{eq:BasisFunctionSeparation}
			\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
		\end{equation}
		where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation and $\boldsymbol{\nu}_{cy}$ is the cut-off frequency of the observed field.
		The field basis function widths can also be inferred using spectral considerations~\cite{Scerri2009}. The basis function width, $\sigma^2_{\phi}$, should be chosen to be
		\begin{align}\label{eq:WidthCutOffRelationship}
		 \sigma^2_{\phi} &= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2} \\
		 \sigma^2_{\nu_{cy}} &= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
		\end{align}}
	\end{block}
	% \vskip2ex
	\begin{block}{Estimation}
		\rmfamily{The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother (URTSS) for state estimation and a least squares (LS) algorithm for parameter estimation.}
		\begin{figure}	
		\begin{center}
		  \includegraphics[width=10in, scale = 10]{EstimationAlgorithm.eps}
		\end{center}
		\caption{{\bf Estimation algorithm}. Flow chart describing steps in algorithm.} 
		\label{fig:Estimation Algorithm}	
		\end{figure} 
	\end{block}	
	\begin{block}{References}
        \small{\rmfamily{\begin{thebibliography}{99}
\bibitem{Deco2008} G. Deco, et al. PLoS Computational Biology. \textbf{4} (2008).
\bibitem{Dewar2009} M. Dewar, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 83-91.
\bibitem{Scerri2009} K. Scerri, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 482-492.
        \end{thebibliography}}}	\end{block}
\end{column}

>>>>

\setbeamercolor{block title}{fg=dblue,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10}
%\setbeamercolor{block title}{fg=red,bg=white}

@@

\institute{1. Department of Electrical and Electronic Engineering, University of Melbourne, Australia \\
2. Department of Automatic Control and Systems Engineering, University of Sheffield, UK \\
3. Department of Applied Physics and Applied Mathematics, Columbia University, USA \\
4. Department of Systems and Control Engineering, University of Malta, Malta }

%-----------------------------------------------------------
% Start the poster itself
%-----------------------------------------------------------
% The \rmfamily command is used frequently throughout the poster to force a serif font to be used for the body text
% Serif font is better for small text, sans-serif font is better for headers (for readability reasons)
%-----------------------------------------------------------
\begin{document}
\begin{frame}[t]
  \begin{columns}[t]												% the [t] option aligns the column's content at the top

@@

		The minimum distance between basis functions must also satisfy 
		\begin{equation}\label{eq:BasisFunctionSeparation}
			\Delta_{\phi} \leq \frac{1}{2\rho_{\phi}\boldsymbol{\nu}_{cy}}
		\end{equation}
		where $\rho_{\phi} \in \mathbb{R} \ge 1$ is an oversampling parameter to determine the basis function separation and $\boldsymbol{\nu}_{cy}$ is the cut-off frequency of the observed field.
		The field basis function widths can also be inferred using spectral considerations~\cite{Scerri2009}. The basis function width, $\sigma^2_{\phi}$, should be chosen to be
		\begin{align}\label{eq:WidthCutOffRelationship}
		 \sigma^2_{\phi} &= \frac{1}{\pi^2\sigma_{\nu_{cy}}^2} \\
		 \sigma^2_{\nu_{cy}} &= \frac{2\boldsymbol\nu_{cy}^\top \boldsymbol\nu_{cy}}{\ln2}.
		\end{align}}
	\end{block}
	% \vskip2ex
	\begin{block}{Estimation}
		\rmfamily{The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother (URTSS) for state estimation and a least squares (LS) algorithm for parameter estimation.}
		\begin{figure}	
		\begin{center}
		  \includegraphics[width=10.5in, scale = 10]{EstimationAlgorithm.eps}
		\end{center}
		\caption{{\bf Estimation algorithm}. Flow chart describing steps in algorithm.} 
		\label{fig:Estimation Algorithm}	
		\end{figure} 
	\end{block}	
	\begin{block}{References}
        \small{\rmfamily{\begin{thebibliography}{99}
\bibitem{Deco2008} G. Deco, et al. PLoS Computational Biology. \textbf{4} (2008).
\bibitem{Dewar2009} M. Dewar, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 83-91.
\bibitem{Scerri2009} K. Scerri, et al. IEEE Trans. on Signal Processing. \textbf{57} (2009) 482-492.
        \end{thebibliography}}}	\end{block}
\end{column}
